Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2018-01-24 papers/integration/omm_integ.tex
Adds Figure N labels to all the figure sections
Changes which should correspond to those made after accepting the Authors proof.

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{James {et~al.}}
\def\Authors{Sebastian James\,$^{1,2}$, Chris Papapavlou\,$^5$, Alexander Blenkinsop\,$^{1,2}$, \\
  Alexander Cope\,$^3$,  \\
  Sean Anderson\,$^{2,4}$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2,*}$}

@@

\def\corrAuthor{Kevin Gurney}
\def\corrAddress{Department of Psychology, The University of Sheffield,
  Western Bank, Sheffield, S10 2TP, UK}
\def\corrEmail{k.gurney@sheffield.ac.uk}

@@

% Change this - we already talked about channels in the context of the
% three channel model shown. Now talk about how we have a map of
% channels - a continuous space in the \ccg model. This can then lead
% on to Fig 3.
\rvwt{The GPR model in Fig.~\ref{fig:ccg_model}(b) has only three
channels, with the focussed inhibition from striatum to SNr and GPe
defined by a simple one-to-one scheme. The action channels represent
discrete, incompatible motor action choices. In the oculomotor model,
an action channel represents the end-point of saccade, and the
competition carried out in the basal ganglia is between potential
saccade end-points. However, eye movements have a \e{continuous}
end-point space; the eye can rotate to any orientation within its
biomechanically permissible range. Some end-points within this range
are mutually exclusive---it's not possible to look to the left and to
the right simultaneously---but \e{nearby} end-points are not
necessarily incompatible. A small enough error in the end-point of a
saccade will not prevent the eye from foveating on a target as the
foveal region of high visual acuity is not infinitesimally small. To
cope with this requirement, the populations within the oculomotor
basal ganglia are conceived of as two-dimensional topographic grids of
leaky integrator neural elements. Activity in each element corresponds
to a spatial location in the visual field. Neighbouring elements
correspond to locations which are close to each other in the visual
field. Focussed one-to-one projections in the GPR model are replaced
by projective fields with many weighted connections. Specifically,
each unit in Str\_D1 projects to a counterpart SNr$_j$ in SNr with
some weight $w_{max}$, but also connects to neighbouring nodes in SNr
with a weight given by $w_{max}.G(d)$, where $G(d)$ is a circularly
symmetric, 2D-Gaussian which is a function of distance $d$ from
SNr$_j$ [Fig.~\ref{fig:ccg_model}(c)]. A similar scheme applies for
the connectivity from Str\_D2 to GPe and for a number of the other
connections in the \ccg~model; in the SpineML implementation of the
model, this connectivity scheme is named `GaussianKernel'.
% NB - having this Fig. ref here is important for figure ordering!
Fig.~\ref{fig:brainmodel} shows a schematic of the SpineML implementation
of the model, based on a diagram produced by SpineCreator. Populations
for Str\_D1, Str\_D2, STN, SNr and GPe are
shown within the `Basal Ganglia' box. Input comes into the model via
the `World' population and the output population is SC\_deep. Compare
this diagram with Figs.~\ref{fig:ccg_model}(a) \&
(b). Fig.~\ref{fig:brainmodel} expands the `SC', `BG' and `slow retinal'
boxes from Fig.~\ref{fig:ccg_model}(a).}

@@

% KM
\rvwt{An illustration of the biomechanical eye model is given in
Figure \ref{fig:bioeye}(a), while Figure \ref{fig:bioeye}(b) depicts
the head model used in the proposed framework.}

@@

% Try to make this clearer for Reviewer 2, Methods Comments, point 5.
\rvwt{To understand the need for this invariance,
consider the effect of a 2D Gaussian hill in SC\_deep which elicits a
successful horizontal saccade of 10\dg. Activity from the 2D Gaussian,
passing through the weight maps will excite the superior and inferior
rectus channels by an equal, balanced amount, so these cancel out,
allowing the eye movement to be horizontal. The amount of activation
passed to the lateral rectus muscle results from a convolution of the
Gaussian and the exponential component of the weight map relationship
in Eq.~\ref{eq:tabareau_eq3}. If the Gaussian hill now appears further
along the collicular surface, coding for a 20\dg~saccade, \e{and also
becomes smaller}, we can still argue that the vertical component
signals to superior/inferior rectus muscles will cancel out, and we
could imagine that the exponential component of
Eq.~\ref{eq:tabareau_eq3} is correctly parameterised to compensate for
the smaller hill. However. Now consider a 2-D Gaussian hill which
codes for a 10\dg~saccade which is `up, and to the right' in equal
proportions. That means that the hill will sit on the boundary between
the weight maps for the `up', and the `right' muscles. Now, if the
hill moves to the $r=\mathrm{20}$\dg~location on the colliculus, \e{and also
reduces in size}, it will excite only the periphery of the sine; the
exponential increase of the map along $r$ is not guaranteed to
compensate for the reduction in the convolution of the Gaussian hill
and the sinusoidal component of the weight map.}
% Add figure for this.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/model_framework.png}
\end{center}
\caption{ The model framework. The model is specified using a combination of
declarative XML files and hand-coded C++. These original model
specifications are shown within the blue box. \bol{b)} The green box shows
the processes which are applied to the model specification to produce
the BRAHMS system. Most of the process is defined within the scripts
which make up \stob, but the hand-written components must be manually
compiled and installed within the BRAHMS Namespace, allowing the
BRAHMS executable to locate them at runtime. \bol{c)} The red box shows the
resulting BRAHMS system ready to be executed by the BRAHMS
executable. In practice, this call is made by \stob.}
\label{fig:modelframework}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/scdeep_plus.png}
\end{center}
\caption{ \bol{a)} \& \bol{b)} Tabareau-style weight maps for `left' and `down' components
of a saccade. \bol{c)} The two weight maps in (a) and (b) shown on the same
graph, viewed from above. Circles show the locations of potential
hills of activity. Purple, dashed circles encode saccades down;
red circles encode saccades with both a left and a down component. \bol{d)}
Showing the additional deep layer of superior colliculus (SC\_deep2)
and the output layer (SC\_avg, named for the fact that in an earlier
version of the model, it received the output of the centroid of
SC\_deep).  The widening Gaussian projection is shown as the arrow
between SC\_deep and SC\_deep2.}
\label{fig:scdeep}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/sacc_vs_targetpos.png}
\end{center}
\caption{ Accuracy of single saccades at different target eccentricities for fixation luminance
0.2 and target luminance 0.3.}
\label{fig:saccvstarg}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=\textwidth]{./figures/weightmaps.png}
\end{center}
\caption{ Weight maps for the connections between the output layer of superior
colliculus and the six long lead burst neurons of the saccadic burst
generator model. Each map increases exponentially with increasing $r$,
multiplied by cosine($\phi$) about its `active' axis.}
\label{fig:weightmaps}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.95\textwidth]{./figures/errorsurface_TModel3.png}
\end{center}
\caption{ The end-point error surface for the original, na\"ive model
(TModel3). \bol{a)} The ratio of the magnitudes of the total error vector
and the target vector, expressed as a percentage. \bol{b)} The ratio of the
magnitude of the $x$ component of the error vector to the magnitude of
the target vector, expressed as a percentage. \bol{c)} As (b) but for the
$y$ component. \bol{d)} As (b), for $z$ component. All colour maps are shown
with the same scale. The target rotations, $\theta_{x}^t$ and
$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.}
\label{fig:errorsurfaceTM3}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.95\textwidth]{./figures/errorsurface.png}
\end{center}
\caption{ The end-point error surface for the model in which a widening
projection field was added to the model of the superior colliculus. \bol{a)}
The ratio of the magnitudes of the total error vector and the target
vector, expressed as a percentage. \bol{b)} The ratio of the magnitude of
the $x$ component of the error vector to the magnitude of the target
vector, expressed as a percentage. \bol{c)} As (b) but for the $y$
component. \bol{d)} As (b), for $z$ component. All colour maps are shown
with the same scale. The target rotations, $\theta_{x}^t$ and
$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.
Note that the range of the colour scale is 0 to 20\%, a much smaller
range than the range in Fig~\ref{fig:errorsurfaceTM3}.}
\label{fig:errorsurface}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/outmany.png}
\end{center}
\caption{ Representative single saccades. \bol{a)} Trajectories from 9 saccades to a
single target at 9 different locations. In each case, a fixation cross
luminance of magnitude 0.2 was displayed at (0,0), the start position
of the eye, until time 0.4~s. The target luminance, magnitude 0.3, was
illuminated at time 0.4~s. Trajectory shape is dependent on the target
position, and there is a variable amount of error in the end-points
achieved by the model. Colour is used in this diagram as an aid to
distinguishing different saccades and their targets; for a given
saccade, the target location is given by the cross of the same colour
closest to the end of the trajectory. \bol{b)} The three rotational
components of the `dark blue' saccade, to target location (-7,-7). \bol{c)} The
three rotational components of the `red' saccade, to target location
(0,-10).}
\label{fig:outmany}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/lat_vs_everything.png}
\end{center}
\caption{ Exploring saccade latencies. \bol{a)} Latency to first movement as a
function of target eccentricity for horizontal targets. \bol{b)} Latency
vs. eccentricity for vertical targets. \bol{c)} Latency vs. gap at three
different luminance values. The data are shown alongside
the \ccg~model results from Fig.~5 of \cite{cope_basal_2017} in blue,
and the experimental results used in that model in red. The fixation
luminance for the \ccg~curve was 0.5, the target luminance 0.6 and
the target eccentricity was 8\dg. The difference between
the \ccg~model data and the data from the current model results from
the different mechanism by which activity in SC\_deep causes a
movement, the differing target angle and the reduced fixation
luminance used here. \bol{d)} The effect
of the dopamine parameter on saccade latencies in gap, step and
overlap conditions, for two different target luminances.  \bol{e)} Saccade
vs. luminance showing gradual transition between reflexive and express
behaviour.
%f) Saccade duration vs. saccade eccentricity for horizontal
%(rightwards), vertical (downwards) and 45\dg~oblique (down \& right) saccades.
}
\label{fig:latvsall}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/outrtn.png}
\end{center}
\caption{ There and back - a saccade to a target, followed by return to the
original fixation. \bol{a)} Out and return saccade to a target at
(0,-10\dg). The outward trajectory is shown in blue, the return in pink.
\bol{b)} Rotational components of the saccade shown in (a). \bol{c)} Outward and
return trajectories for the saccade shown in (a) alongside saccades to
three other targets.}
\label{fig:outrtn}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/doublesteps.png}
\end{center}
\caption{ Double steps. The effect of illuminating a first target at 8\dg~or
12\dg, followed by a second target at 12\dg~or 8\dg. \bol{a)} Horizontal
rotation of the eye plotted vs.~time for a saccade to the 12\dg~target
only (red), and to an 8\dg~target at 0.4~s followed by a 12\dg~target
after 30~ms (blue) or 40~ms (black). The timings are indicated by
vertical lines. When the second target is presented up to 30~ms after
the initial target, the initial target has not had time to dominate
the output saccade and a saccade to a location close to the second
target is made. If the delay is 40~ms or more, the activity from the
initial target has time to cause a built up of actiivty in SC\_deep
and an initial saccade close to the first target is made, followed,
after a longer than usual latency period, with a second saccade closer
to the second target. In this graph, the mean of five separate
simulations is plotted along with $\pm$1 standard deviation around the
mean. \bol{b)} The $\theta_{x}$/$\theta_{y}$ trajectories corresponding to
the data presented in (a).}
\label{fig:doublesteps}
\end{figure}

>>>>

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{James {et~al.}}
\def\Authors{Sebastian S.~James\,$^{1,2}$, Chris Papapavlou\,$^5$, Alexander Blenkinsop\,$^{1,2}$, \\
  Alexander J.~Cope\,$^3$,  \\
  Sean Anderson\,$^{2,4}$, Konstantinos Moustakas\,$^5$, Kevin N.~Gurney\,$^{1,2,*}$}

@@

\def\corrAuthor{Kevin N.~Gurney}
\def\corrAddress{Department of Psychology, The University of Sheffield,
  Western Bank, Sheffield, S10 2TP, UK}
\def\corrEmail{k.gurney@sheffield.ac.uk}

@@

% Change this - we already talked about channels in the context of the
% three channel model shown. Now talk about how we have a map of
% channels - a continuous space in the \ccg model. This can then lead
% on to Fig 3.
\rvwt{The GPR model in Fig.~\ref{fig:ccg_model}(b) has only three
channels, with the focussed inhibition from striatum to SNr and GPe
defined by a simple one-to-one scheme. The action channels represent
discrete, incompatible motor action choices. In the oculomotor model,
an action channel represents the end-point of saccade, and the
competition carried out in the basal ganglia is between potential
saccade end-points. However, eye movements have a \e{continuous}
end-point space; the eye can rotate to any orientation within its
biomechanically permissible range. Some end-points within this range
are mutually exclusive---it's not possible to look to the left and to
the right simultaneously---but \e{nearby} end-points are not
necessarily incompatible. A small enough error in the end-point of a
saccade will not prevent the eye from foveating on a target as the
foveal region of high visual acuity is not infinitesimally small. To
cope with this requirement, the populations within the oculomotor
basal ganglia are conceived of as two-dimensional topographic grids of
leaky integrator neural elements. Activity in each element corresponds
to a spatial location in the visual field. Neighbouring elements
correspond to locations which are close to each other in the visual
field. Focussed one-to-one projections in the GPR model are replaced
by projective fields with many weighted connections. Specifically,
each unit in Str\_D1 projects to a counterpart SNr$_j$ in SNr with
some weight $w_{max}$, but also connects to neighbouring nodes in SNr
with a weight given by $w_{max}.G(d)$, where $G(d)$ is a circularly
symmetric, 2D-Gaussian which is a function of distance $d$ from
SNr$_j$ [Figs.~\ref{fig:ccg_model}(c)\&(d)]. A similar scheme applies for
the connectivity from Str\_D2 to GPe and for a number of the other
connections in the \ccg~model; in the SpineML implementation of the
model, this connectivity scheme is named `GaussianKernel'.
% NB - having this Fig. ref here is important for figure ordering!
Fig.~\ref{fig:brainmodel} shows a schematic of the SpineML implementation
of the model, based on a diagram produced by SpineCreator. Populations
for Str\_D1, Str\_D2, STN, SNr and GPe are
shown within the `Basal Ganglia' box. Input comes into the model via
the `World' population and the output population is SC\_deep. Compare
this diagram with Figs.~\ref{fig:ccg_model}(a) \&
(b). Fig.~\ref{fig:brainmodel} expands the `SC', `BG' and `slow retinal'
boxes from Fig.~\ref{fig:ccg_model}(a).}

@@

% KM
\rvwt{An illustration of the biomechanical eye model is given in
Figure \ref{fig:bioeye}(a), while Figure \ref{fig:bioeye}(b) depicts
the head model used in the proposed
framework. Figure \ref{fig:bioeye}(c) shows a cross-sectional view of
the eye and the spherical screen on which targets were projected.}

@@

% Try to make this clearer for Reviewer 2, Methods Comments, point 5.
\rvwt{To understand the need for this invariance,
consider the effect of a 2D Gaussian hill in SC\_deep which elicits a
successful horizontal saccade of 10\dg~using the weight maps shown in
Figures 7(a)--(c). Activity from the 2D Gaussian (schematically
represented as the large purple dashed circle in Figure 7C),
passing through the weight maps will excite the superior (not shown) and inferior
rectus [Figure 7(b)] channels by an equal, balanced amount, so these cancel out,
allowing the eye movement to be horizontal. The amount of activation
passed to the lateral rectus muscle results from a convolution of the
Gaussian and the exponential component of the weight map relationship
in Eq.~\ref{eq:tabareau_eq3}. If the Gaussian hill now appears further
along the collicular surface, coding for a 20\dg~saccade, \e{and also
becomes smaller} (small purple dashed circle), we can still argue that the vertical component
signals to superior/inferior rectus muscles will cancel out, and we
could imagine that the exponential component of
Eq.~\ref{eq:tabareau_eq3} is correctly parameterised to compensate for
the smaller hill. Now consider a 2-D Gaussian hill which
codes for a 10\dg~saccade which is `down, and to the left' in equal
proportions (large red circle). That means that the hill will sit on the boundary between
the weight maps for the `down', and the `left' muscles. Now, if the
hill moves to the $r=\mathrm{20}$\dg~location on the colliculus (small
red circle), \e{and also
reduces in size}, it will excite only the periphery of the sine; the
exponential increase of the map along $r$ is not guaranteed to
compensate for the reduction in the convolution of the Gaussian hill
and the sinusoidally varying component of the weight map along the $\phi$ axis in
Figure 7(a).}
% Add figure for this.

@@

% Figure 6
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/model_framework.png}
\end{center}
\caption{ The model framework. \bol{a)} The model is specified using a combination of
declarative XML files and hand-coded C++. These original model
specifications are shown within the blue box. \bol{b)} The green box shows
the processes which are applied to the model specification to produce
the BRAHMS system. Most of the process is defined within the scripts
which make up \stob, but the hand-written components must be manually
compiled and installed within the BRAHMS Namespace, allowing the
BRAHMS executable to locate them at runtime. \bol{c)} The red box shows the
resulting BRAHMS system ready to be executed by the BRAHMS
executable. In practice, this call is made by \stob.}
\label{fig:modelframework}
\end{figure}

% Figure 7
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/scdeep_plus.png}
\end{center}
\caption{ \bol{a)} \& \bol{b)} Tabareau-style weight maps for `left' and `down' components
of a saccade. \bol{c)} The two weight maps in (a) and (b) shown on the same
graph, viewed from above. Circles show the locations of potential
hills of activity. Purple, dashed circles encode saccades left;
red circles encode saccades with both a left and a down component. \bol{d)}
Showing the additional deep layer of superior colliculus (SC\_deep2)
and the output layer (SC\_avg, named for the fact that in an earlier
version of the model, it received the output of the centroid of
SC\_deep).  The widening Gaussian projection is shown as the arrow
between SC\_deep and SC\_deep2.}
\label{fig:scdeep}
\end{figure}

% Figure 8
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/sacc_vs_targetpos.png}
\end{center}
\caption{ Accuracy of single saccades at different target eccentricities for fixation luminance
0.2 and target luminance 0.3. \bol{a)} Horizontal rotations about the
y axis. \bol{b)} Vertical rotations of the eye about the x axis.}
\label{fig:saccvstarg}
\end{figure}

% Figure 9
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=\textwidth]{./figures/weightmaps.png}
\end{center}
\caption{ Weight maps for the connections between the output layer of superior
colliculus and the six long lead burst neurons of the saccadic burst
generator model. Each map increases exponentially with increasing $r$,
multiplied by cosine($\phi$) about its `active' axis. \bol{a)} Weight
map for leftward movements which innervates the lateral rectus in this
single left-eye model. \bol{b)} Map for downward movements; innervates
the inferior rectus. \bol{c)} Superior oblique muscle weight
map. \bol{d)} Weight map for rightward movements/medial rectus
muscle. \bol{e)} Weight map for the superior rectus muscle which
generates upward movements. \bol{f)} Inferior oblique map.}
\label{fig:weightmaps}
\end{figure}

% Figure 10
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.95\textwidth]{./figures/errorsurface_TModel3.png}
\end{center}
\caption{ The end-point error surface for the original, na\"ive model
(TModel3). \bol{a)} The ratio of the magnitudes of the total error vector
and the target vector, expressed as a percentage. \bol{b)} The ratio of the
magnitude of the $x$ component of the error vector to the magnitude of
the target vector, expressed as a percentage. \bol{c)} As (b) but for the
$y$ component. \bol{d)} As (b), for $z$ component. All colour maps are shown
with the same scale. The target rotations, $\theta_{x}^t$ and
$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.}
\label{fig:errorsurfaceTM3}
\end{figure}

% Figure 11
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.95\textwidth]{./figures/errorsurface.png}
\end{center}
\caption{ The end-point error surface for the model in which a widening
projection field was added to the model of the superior colliculus. \bol{a)}
The ratio of the magnitudes of the total error vector and the target
vector, expressed as a percentage. \bol{b)} The ratio of the magnitude of
the $x$ component of the error vector to the magnitude of the target
vector, expressed as a percentage. \bol{c)} As (b) but for the $y$
component. \bol{d)} As (b), for $z$ component. All colour maps are shown
with the same scale. The target rotations, $\theta_{x}^t$ and
$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.
Note that the range of the colour scale is 0 to 20\%, a much smaller
range than the range in Fig~\ref{fig:errorsurfaceTM3}.}
\label{fig:errorsurface}
\end{figure}

% Figure 12
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/outmany.png}
\end{center}
\caption{ Representative single saccades. \bol{a)} Trajectories from 9 saccades to a
single target at 9 different locations. In each case, a fixation cross
luminance of magnitude 0.2 was displayed at (0,0), the start position
of the eye, until time 0.4~s. The target luminance, magnitude 0.3, was
illuminated at time 0.4~s. Trajectory shape is dependent on the target
position, and there is a variable amount of error in the end-points
achieved by the model. Colour is used in this diagram as an aid to
distinguishing different saccades and their targets; for a given
saccade, the target location is given by the cross of the same colour
closest to the end of the trajectory. \bol{b)} The three rotational
components of the `dark blue' saccade, to target location (-7,-7). \bol{c)} The
three rotational components of the `red' saccade, to target location
(0,-10).}
\label{fig:outmany}
\end{figure}

% Figure 13
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/lat_vs_everything.png}
\end{center}
\caption{ Exploring saccade latencies. \bol{a)} Latency to first movement as a
function of target eccentricity for horizontal targets. \bol{b)} Latency
vs. eccentricity for vertical targets. \bol{c)} Latency vs. gap at three
different luminance values. The data are shown alongside
the \ccg~model results from Fig.~5 of \cite{cope_basal_2017} in blue,
and the experimental results used in that model in red. The fixation
luminance for the \ccg~curve was 0.5, the target luminance 0.6 and
the target eccentricity was 8\dg. The difference between
the \ccg~model data and the data from the current model results from
the different mechanism by which activity in SC\_deep causes a
movement, the differing target angle and the reduced fixation
luminance used here. \bol{d)} The effect
of the dopamine parameter on saccade latencies in gap, step and
overlap conditions, for two different target luminances.  \bol{e)} Saccade
vs. luminance showing gradual transition between reflexive and express
behaviour.
%f) Saccade duration vs. saccade eccentricity for horizontal
%(rightwards), vertical (downwards) and 45\dg~oblique (down \& right) saccades.
}
\label{fig:latvsall}
\end{figure}

% Figure 14
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/outrtn.png}
\end{center}
\caption{ There and back - a saccade to a target, followed by return to the
original fixation. \bol{a)} Out and return saccade to a target at
(0,-10\dg). The outward trajectory is shown in blue, the return in pink.
\bol{b)} Rotational components of the saccade shown in (a). \bol{c)} Outward and
return trajectories for the saccade shown in (a) alongside saccades to
three other targets.}
\label{fig:outrtn}
\end{figure}

% Figure 15
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/doublesteps.png}
\end{center}
\caption{ Double steps. The effect of illuminating a first target at 8\dg~or
12\dg, followed by a second target at 12\dg~or 8\dg. \bol{a)} Horizontal
rotation of the eye plotted vs.~time for a saccade to the 12\dg~target
only (red), and to an 8\dg~target at 0.4~s followed by a 12\dg~target
after 30~ms (blue) or 40~ms (black). The timings are indicated by
vertical lines. When the second target is presented up to 30~ms after
the initial target, the initial target has not had time to dominate
the output saccade and a saccade to a location close to the second
target is made. If the delay is 40~ms or more, the activity from the
initial target has time to cause a built up of actiivty in SC\_deep
and an initial saccade close to the first target is made, followed,
after a longer than usual latency period, with a second saccade closer
to the second target. In this graph, the mean of five separate
simulations is plotted along with $\pm$1 standard deviation around the
mean. \bol{b)} The $\theta_{x}$/$\theta_{y}$ trajectories corresponding to
the data presented in (a).}
\label{fig:doublesteps}
\end{figure}
